A generalization of Plackett-Luce likelihoods to incorporate non-independence of competitors

### 2023-01-06 inst/plackett_luce_monster.Rmd
clarification and partial correction

* Runner $i$ might wish to support $j$.  If runner $i$ finishes, once
  his rank is established he might be able to help $j$ in some way.
  He might cheer his still-running friend.  In general, we can
  consider $n$ ordered pairs $(i_r,j_r)$, $1\leq r\leq n$, with runner
  $i_1$ helping runner $j_1$, runner $i_2$ helping $j_2$, and so on.
  One simple case would be equivalence classes of
  $[n]=\{1,2,\ldots,n\}$ with each equivalence class comprising
  mutually supporting runners.  In this model, with a pair of mutually
  supporting runners only the higher-placed competitor can affect the
  other.  Each equivalence class might have a different supportive
  proclivity.

>>>>

* Runner $i$ might wish to support $j$.  If runner $i$ finishes, once
  his rank is established he might be able to help $j$ in some way.
  He might cheer his still-running friend, spurring him to run faster
  and augmenting his competitive strength.

* In general, we can consider $n$ ordered pairs $(i_r,j_r)$, $1\leq
  r\leq n$, with runner $i_1$ helping runner $j_1$, runner $i_2$
  helping $j_2$, and so on.  One simple case would be equivalence
  classes of $[n]=\{1,2,\ldots,n\}$ with each equivalence class
  comprising mutually supporting runners.  In this model, with a pair
  of mutually supporting runners only the higher-placed competitor can
  affect the other.  Each equivalence class might have a different
  supportive proclivity.
